 \documentclass[a4paper,english]{article}

\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage[T1]{fontenc}
\pagestyle{empty}
\usepackage{graphicx}

\usepackage[pdftex,
            colorlinks=true,
            pdfstartview=FitV,
            linkcolor=blue,
            citecolor=blue,
            urlcolor=blue,]{hyperref}
\hypersetup{pdfauthor = {Hugo Peres Castilho},
            pdftitle = {Curriculum Vitae},
            pdfsubject = {Hugo Peres Castilho},
            pdfkeywords = {CV, Curriculum Vitae, Hugo Castilho, Hugo P.
Castilho, Hugo Castilho}}

\newcommand{\nome}[1]{
\hspace{-7mm}{\huge \textbf{ #1}} \vspace{-1.6mm}\\
\rule{\columnwidth}{.5mm} \vspace{-7.7mm}\\
\rule{\columnwidth}{.25mm}
}

\newcommand{\topic}[1]{
\section*{#1} \vspace{-6mm}
\rule{\columnwidth}{.25mm}
}

\begin{document}

\nome{Hugo Peres Castilho}
\begin{flushright}
    \begin{tabular}{lcl}
        \input{contact.tex}
    \end{tabular}
\end{flushright}

\topic{Education}
\begin{itemize}
\setlength{\itemsep}{-1mm}
    \item[] Physics Engineering
    \item[] Instituto Superior Técnico, Lisboa -- Portugal
    \item[] 1999--2001
\end{itemize}
\begin{itemize}
\setlength{\itemsep}{-1mm}
    \item[] Mechanical Engineering
    \item[] Robotics and Automation Branch
    \item[] Instituto Superior Técnico, Lisboa -- Portugal
    \item[] Finished on Nov/2006
\end{itemize}

\topic{Professional Background}
\vspace{0.5cm}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] {\bf INETI}
        \item[] Instituto Nacional de Engenharia, Tecnologia e Inovação
        \item[] Sep/2005--May/2007
        \item[] www.ineti.pt
    \end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] Industry focused research and development
        \item[] CLIMA -- Real-time fabric defect detection
        \item[] 3D laser inspection of mechanical parts
    \end{itemize}
\end{minipage}
\vspace{0.5cm}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] {\bf Robosavvy}
        \item[] Mar/2007--Dec/2007
        \item[] www.robosavvy.com
    \end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] Software development
        \item[] Humanoid robotics physics simulation platform
    \end{itemize}
\end{minipage}
\vspace{0.5cm}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] {\bf Rose Real Estate}
        \item[] Aug/2007--Jan/2009
        \item[] rrr.pt
    \end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] Website development and maintenance
    \end{itemize}
\end{minipage}
\vspace{0.5cm}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] {\bf CERN}
        \item[] European Organization for Nuclear Research
        \item[] Dec/2007--Nov/2008
        \item[] www.cern.ch
    \end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] Software development, research, team coordination.
        \item[] FPIAA (Finding People in Atlas Areas) -- Personnel tracking system for critical ATLAS areas.
        \item[] ATLAS DCS Web Interface -- Detector monitoring system, web interface.
    \end{itemize}
\end{minipage}
\vspace{0.5cm}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] {\bf Infolau}
        \item[] Nov/2008--Dev/2012
        \item[] www.infolau.com
    \end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] Software development
        \item[] Crédito Agricola -- Credit card back-end development and maintenance
    \end{itemize}
\end{minipage}
\vspace{0.5cm}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] {\bf MyWishGuru}
        \item[] Nov/2012--Present
        \item[] www.mywishguru.com
    \end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
    \begin{itemize}
    \setlength{\itemsep}{-1mm}
        \item[] Lead Developer
        \item[] Front and back end development
        \item[] Python project on Google Appengine
    \end{itemize}
\end{minipage}

\topic{Publications}
\begin{itemize}
    \item[] Hugo P. Castilho, João R. C. Pinto, António L. Serafim, "NN
Automated Defect Detection Based on Optimized Thresholding", ICIAR 2006 -
Intern. Conf. on Image Analysis and Recognition 2006, Póvoa
de Varzim, Portugal; Lecture Notes in Computer Science, Springer Verlag,
LNCS 41423, Vol.2, pp. 790-801.
    \item[] Hugo P. Castilho, Paulo J. S. Gonçalves, João R. C. Pinto, António
L. Serafim, "Intelligent Real-Time Fabric Defect Detection", ICIAR
2007, Montreal, Canada; Lecture Notes in Computer Science, Springer Verlag,
LNCS 4633, pp. 1309-1319.
    \item[] Hugo P. Castilho, António L. Serafim, João R. C. Pinto, "Automated
fabric defect detection: A real-time NN approach" , Publication Lisboa: INETI - 
Memoirs, 2006/2007, 2007.
\end{itemize}

\topic{Programming Languages}
\begin{itemize}
\setlength{\itemsep}{-1mm}
    \item C/C++
    \item C\#
    \item Java
    \item Javascript
    \item Matlab
    \item MUMPS/PSL PROFILE
    \item Python
    %\item PVSS (SCADA)
\end{itemize}

\topic{Application/Framework Experience}
\begin{itemize}
\setlength{\itemsep}{-1mm}
    \item Version Control: Subversion, CVS and git
    \item Google App Engine Framework
    \item SQL
    \item HTML
    \item CSS, Sass and Less
    \item Django
    \item OpenCV
    %\item Pygame--Game development python framework
    %\item Box2D--2D physics engine
    %\item Mathematica
    %\item Latex
    %\item Solid Edge
\end{itemize}

\topic{Languages}

\begin{tabular}{llll}
Language & Understanding & Speaking & Writing \\
\hline
Portuguese & Advanced & Advanced & Advanced \\
English & Advanced & Advanced & Advanced \\
%French & Medium & Basic & Very Basic \\
%Spanish & Medium & Basic & None \\
\end{tabular}


\end{document}
